The Courtroom Challenge—A Conjecture on the Unavoidable Cost of LLM Verification

### 2025-06-20 paper/main.tex
Add files via upload

% =========================================================
\begin{document}
\maketitle
\begin{abstract}
  Large language models hallucinate; ad-hoc patches conceal the true cost of verification. 
  We therefore pose a falsifiable ultimatum: either automate validation, prove it unnecessary, or pay the explicit human-in-the-loop cost.  
  Conjecture 1 (the Courtroom Challenge). 
  For any unbounded open-world text stream, a system that lacks both (i) a persistent precedent store and (ii) a friction-priced validation loop will accumulate unbounded prequential regret.
  We formalise the state machine, cost ledger, and impossibility triangle that make this conjecture testable, and invite the community to break it.
  A 100-query toy stream illustrates how the ledger is logged\footnote{Baseline script will appear at \url{https://github.com/johnrepsys/courtroom-model} with v2.}; no attempt is made here to optimise the validator.
  In addition, we present the Courtroom Model, a wrapper architecture that subjects every LLM claim to a perpetual cycle of precedent search, automated semantic checks, and selective escalation to an external judge—human or automated.
  Each new output is validated against a persistent vector memory, while conflicting evidence triggers the re-examination of prior “case law.”
  The challenge stands: thrive in an open world without paying the validation bill—or show why the bill is inescapable.
\end{abstract}

>>>>

% =========================================================
\begin{document}
\maketitle
\begin{abstract}
  Large language models hallucinate; ad-hoc patches conceal the true cost of verification. 
  We therefore pose a falsifiable ultimatum: either automate validation, prove it unnecessary, or pay the explicit human-in-the-loop cost.  
  Conjecture 1 (the Courtroom Challenge). 
  For any unbounded open-world text stream, a system that lacks both (i) a persistent precedent store and (ii) a friction-priced validation loop will accumulate unbounded prequential regret.
  We formalise the state machine, cost ledger, and impossibility triangle that make this conjecture testable, and invite the community to break it.
  A 100-query toy stream illustrates how the ledger is logged\footnote{Baseline script is shown at \url{https://github.com/johnrepsys/courtroom-model}.}; no attempt is made here to optimise the validator.
  In addition, we present the Courtroom Model, a wrapper architecture that subjects every LLM claim to a perpetual cycle of precedent search, automated semantic checks, and selective escalation to an external judge—human or automated.
  Each new output is validated against a persistent vector memory, while conflicting evidence triggers the re-examination of prior “case law.”
  The challenge stands: thrive in an open world without paying the validation bill—or show why the bill is inescapable.
\end{abstract}
